Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2018-01-02 paper/main.tex
Update paper to use new plots

\begin{figure}
  \centering
  \begin{minipage}{0.5\textwidth}
    \includegraphics[width=1.0\textwidth]{./1k_synthetic_new.png}
  \end{minipage}%
    \begin{minipage}{0.5\textwidth}
    \includegraphics[width=1.0\textwidth]{./8k_synthetic_new.png}
  \end{minipage}
  \begin{minipage}{0.5\textwidth}
    \includegraphics[width=1.0\textwidth]{./1m_synthetic_new.png}
  \end{minipage}
  \caption{Learning curves for GILR-LSTM and CuDNN LSTM architectures for various
    sequence lengths. Each plot includes learning curves from multiple independent
    runs. The shaded area around each learning curve shows the rolling variance
    of the loss over minibatches within the run.
}
    \label{fig:synthetic_training}
  \end{figure}

>>>>

\begin{figure}
  \centering
  \begin{minipage}{0.5\textwidth}
    \includegraphics[width=1.0\textwidth]{./between_chain_plots/1k_20_smoothing.png}
  \end{minipage}%
    \begin{minipage}{0.5\textwidth}
    \includegraphics[width=1.0\textwidth]{./between_chain_plots/8k_5_smoothing.png}
  \end{minipage}
  \begin{minipage}{0.5\textwidth}
    \includegraphics[width=1.0\textwidth]{./between_chain_plots/1m_20_smoothing.png}
  \end{minipage}
  \caption{Learning curves for GILR-LSTM and CuDNN LSTM architectures for various
    sequence lengths. Each plot shows the moving mean and standard deviation of
    classification accuracy over five training runs, with the exception of a single
    run for CuDNN LSTM on 1 million sequence length.}
    \label{fig:synthetic_training}
  \end{figure}
